WTCIII-Figures

### 2015-06-24 markdown/WTC3_figures.Rmd
lots of stuff done!!!!!!
made more manuscript figures in master folder

moved more scripts out of master folder

added figures to markdown figures rmd

updated packages script so it is universal for scripts and markdowns

added new labels to plot objects

![ciN](ppfd.png)

* Figure 1. Here is the light environment in which gas exchange measurements for sun and shade leaves were measured.

This data was generated with a handheld par sensor for each individual leaf and verified with ceptometer readings within the canopy at the height of the measured leaf. There was a ~75% reduction in PPFD from sun to shave leaves.

@@

* ACi curves were measured at saturating light for both sun and shade leaves. Both Vc<sub>max</sub> and J<sub>max</sub> are reduced in shade leaves with little effect of the temperature treatment(AT/ET). ACi curves were taken once towards the end of the experiment on well watered trees

>>>>

```{r knitr_options , include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=6,
echo=FALSE, message=FALSE,
fig.align='center', warning=FALSE)
```

```{r, results='asis'}
library(knitr)
opts_knit$set(root.dir = '../')
```

```{r global data/sourcing , include=FALSE}
source("functions and packages/functions.R")
source("functions and packages/packages.R")
source("master_scripts/plot_objects.R")
library(pander)

par <- read.csv("raw data/par.csv")
treatments <- read.csv("raw data/chamber_trt.csv")

```

#### <u>Design</u>
* WTCIII was a warming experiment with ambient and +3°C warming (n=6).  A drought manipulation was added in the last few months of the experiment but is not included here.
* Sun leaves were measured in the upper canopy at their current PPFD.  Shade leaves were measured in the lower/middle canopy, first at their current PPFD and then again at sun leaf PPFD.
* New fully expanded leaves were measured. Shade leaves were sampled into the middle canopy as the experiment progressed to avoid issues with leaf age.
* Leaf physiological measurements were taken at their current temperature (ambient, +3°C). Thus, data below represent a large range of temperatures from ~18-35°C.

```{r par, fig.width=12, fig.height=6}
source("master_scripts/par.R")
```

* Figure 1. Local light environment for sun and shade leaves for each gas exchange campaign. Means and standard errors represent 1m intregrated PPFD (n=5), measured with a ceptometer, at the canopy height of each selected leaf.

There was a ~75% reduction in PPFD from sun to shave leaves.

@@

* Figure2. Predicted photosynthetic CO2 response (ACi))curves for sun and shade leaves at elevated and ambient temperature treatments. Aci curves were developed at 25C and at saturating light (1800 umols m^-1 s^-1). ACi curves were taken once on well watered trees before the initation of the drought treatment.

```{r, results='asis'}
aci_leaf <- read.csv("calculated_data/tdl_aci.csv")
names(aci_leaf) <-c("Leaf", "Temperature", "Vcmax", "Jmax", "Vcmax_se", "Jmax_se")

aci_leaf2 <- aci_leaf[,c(1,2,3,5,4,6)]

panderOptions("digits", 3)
pander(aci_leaf2, caption="Leaf Biochemistry")
```

![wateruse](wateruse.png)

* Figure 3. Response of instantaneous water use efficiency (ITE) to leaf vapor pressure deficit (VPD) (a) and response of leaf photosynthesis rates to stomatal conductance (b) for sun and shade leaves at elevated and ambient temperature treatments. For (a)  lines represent predictions from the optimal ITE model with k=0.05 and a specific g1 value for each leaf type and treatment. For (b) lines represent 95% confidence intervals from a general additive model with k=5.

![c13N](c13_nitro.png)

* Figure 4. The relationship between leaf c13 and nitrogen[area] for sun and shade leaves at elevated and ambient temperature treatments.

```{r gm, fig.width=8, fig.height=10}
source("master_scripts/gm_figures.R")
```

* Figure 5. Response of mesophyll conductance to leaf temperature (a) and the response of leaf photosynthesis to mesophyll conductance (b) for sun and shade leaves at elevated and ambient temperature treatments.  The mean difference in mesophyll conductance (c) and photosyntheis (d) between sun and shade leaves with standard errors.  For (a) and (b) lines represent 95% confidence intervals generated with bootstrapping methods (n=999) from mixed effect linear model equations with chambers as a random effect.

```{r lights, fig.width=8, fig.height=10}
source("master_scripts/gm_lightson.R")
```

* Figure 6. Response of photosynthesis to mesophyll conductance following a maximum sunfleck response of shade leaves (a) and the mean difference in mesophyll conductance (c) and photosyntheis (d) to sun flecks in shade leaves with standard errors.  The sunfleck was simulated by increasing the PPFD to the level of the sun leaf in the same chamber.  The response of leaf physiology to sun flecks was recorded once both photosynthesis and stomatal conductance were stable in the gas exchange cuvette (ca. 25m).
